Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-01 report.Rmd
sp analysis
cv
update

![](figs/lalt_sep_grid.png)

# SMA table (species-level)

```{r}
tar_load(sma_tab)
sma_tab |>
  kable() |>
  kable_styling()
```

>>>>

## MCMC check

```{r}
targets::tar_load("fit_sp_0_summary_simple")
targets::tar_load("fit_sp_1_summary_model")
targets::tar_load("fit_sp_2_summary_model")
targets::tar_load("fit_sp_3_summary_model")
targets::tar_load("fit_sp_4_summary_sma")
# targets::tar_load("fit_sp_5_summary_sma")
targets::tar_load("fit_sp_6_summary_sma_err")

targets::tar_load("fit_sp_0_diagnostics_simple")
targets::tar_load("fit_sp_1_diagnostics_model")
targets::tar_load("fit_sp_2_diagnostics_model")
targets::tar_load("fit_sp_3_diagnostics_model")
targets::tar_load("fit_sp_4_diagnostics_sma")
# targets::tar_load("fit_sp_5_diagnostics_sma")
targets::tar_load("fit_sp_6_diagnostics_sma_err")
```

```{r}
fit_sp_0_summary_simple |> filter(rhat > 1.1)
fit_sp_1_summary_model |> filter(rhat > 1.1)
fit_sp_2_summary_model |> filter(rhat > 1.1)
fit_sp_3_summary_model |> filter(rhat > 1.1)
fit_sp_4_summary_sma |> filter(rhat > 1.1)
# fit_sp_5_summary_sma |> filter(rhat > 1.1)
fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
```

It is difficult to model heteroskedasticity and measurement errors at the same time.

```{r}
div_check(fit_sp_0_diagnostics_simple)
div_check(fit_sp_1_diagnostics_model)
div_check(fit_sp_2_diagnostics_model)
div_check(fit_sp_3_diagnostics_model)
div_check(fit_sp_4_diagnostics_sma)
# div_check(fit_sp_5_diagnostics_sma)
div_check(fit_sp_6_diagnostics_sma_err)
```

```{r}
targets::tar_load(loo_model)
loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]], loo_model[[4]])
```

```{r}
tar_read(cv_sp)
```

## coef

```{r, eval=TRUE}
tar_load(coef_sp_png)
```

![](figs/coef_sp.png)

```{r, eval=TRUE}
tar_load(coef_sp_png2)
```

![](figs/coef_sp2.png)

```{r, eval=TRUE}
tar_load(coef_sp_png3)
```

![](figs/coef_sp3.png)

# SMA table

## species

```{r, eval=TRUE}
tar_load(sma_sp_tab)
sma_sp_tab |>
  kable() |>
  kable_styling()
```

## species LD

```{r, eval=TRUE}
tar_load(sma_sp_ld_tab)
sma_sp_ld_tab |>
  kable() |>
  kable_styling()
```

## tree

```{r, eval=TRUE}
tar_load(sma_tree_tab)
sma_tree_tab |>
  kable() |>
  kable_styling()
```

## tree LD

```{r, eval=TRUE}
tar_load(sma_tree_ld_tab)
sma_tree_ld_tab |>
  kable() |>
  kable_styling()
```

# Validation

```{r}
tar_load(cv_sp)
cv_sp
```

```{r}
tar_load(cv_tree)
cv_tree
```
